\documentclass[12pt, a4paper]{article}


\usepackage{amsmath}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{C Programming Examination}
\fancyhead[R]{Semester I, MCA}
\fancyfoot[C]{\thepage}


\title{\textbf{C Programming Examination}}
\author{MCA 1st Year \\ Dibrugarh University}
\date{\today}

\begin{document}

\maketitle


\section*{Instructions}
\begin{itemize}
    \item The exam duration is 3 hours.
    \item Attempt all questions.
    \item Write your answers neatly and clearly.
    \item Marks are indicated in brackets next to each question.
\end{itemize}



    
\section*{Section A: Objective Type Questions (1 mark each)}
Answer all questions. Each question carries 1 mark.

\begin{enumerate}
    \item Which of the following is a correct syntax for a for-loop in C?
    \begin{enumerate}
        \item \texttt{for(i=0; i<n; i++)}
        \item \texttt{for i=0; i<n; i++}
        \item \texttt{for(i=0: i<n: i+)}
        \item \texttt{for i=0: i<n: i++}
    \end{enumerate}

    \item What is the output of the following code?
    \begin{verbatim}
        int x = 5;
        printf("%d", x++);
    \end{verbatim}
    \begin{enumerate}
        \item 4
        \item 5
        \item 6
        \item Compiler Error
    \end{enumerate}

    \item Which of these is not a valid variable name in C?
    \begin{enumerate}
        \item \texttt{int\_number}
        \item \texttt{\_int}
        \item \texttt{2number}
        \item \texttt{number2}
    \end{enumerate}

  
\end{enumerate}


\section*{Section B: Short Answer Questions (5 marks each)}
Answer any four questions. Each question carries 5 marks.

\begin{enumerate}
    \item Explain the use of pointers in C programming. Give an example.
    \item What is a structure in C? Write a code example to demonstrate defining and accessing a structure.
    \item Describe the difference between \texttt{while} and \texttt{do-while} loops with an example.
    \item Write a C program to find the largest element in an array of integers.
    \item Explain the concept of recursion in C with an example.
   
\end{enumerate}


\section*{Section C: Long Answer Questions (10 marks each)}
Answer any two questions. Each question carries 10 marks.

\begin{enumerate}
    \item Write a C program that takes a number as input and checks if it is a prime number. Explain your code.
    \item Discuss file handling in C programming. Write a program to read and write data to a file.
    \item Explain dynamic memory allocation in C. Write a program that demonstrates the use of \texttt{malloc} and \texttt{free}.
    \item Write a C program to perform matrix multiplication and explain the code.
   
\end{enumerate}

\end{document}